Rewrite the following for a resume to Texas Instrumenst based of the work they do!

\subsection{Connection to NVIDIA' primary research domains}

While simple parallel algorithms seem intuitive and straightforward, they often exhibit poor performance as they struggle to exploit the full potential of modern hardware. Well designed parallel algorithms, however, are inherently complex \cite{cuda-garland08}. Developing efficient parallel dynamic graph algorithms that yield significant performance gains (instead of relying solely on hardware improvements) is likely to be useful to technology companies, banks/financial institutions, government agencies, and researchers. This aligns with NVIDIA's focus on making accelerated computing accessible to a large number of people working on solving the world's toughest problems.

\ignore{This complexity arises from the need to manage concurrency, optimize data access patterns, and the need to minimize contention for resources, synchronization overhead, false sharing, and load imbalance \cite{par-shaw98}. In addition, graph algorithms often exhibit irregular memory access patterns, making it challenging to achieve efficient parallelization \cite{mem-murphy07, gpu-burtscher12}.\ignore{Technology companies use graph algorithms for social networks to improve their web search, recommender systems, and identify fake news. Banks and credit card companies use them to prevent fraud. Government agencies use them to investigate criminal activity and terrorist networks. Researchers in a variety of fields, such as biology, social science, and computer science, use them to study complex systems. Subhajit is interested in the design Efficient algorithms for Dynamic Social Networks, that minimize the work needed to obtain high-quality results, and make effective use of parallelism.} This aligns with NVIDIA's focus on accelerated computing and its applications.\ignore{ His anticipated future investigations include exploring dynamic graph algorithms for the PageRank and community detection problems in streaming and distributed settings, exploring similarity measures, such as SimRank and Personalized PageRank (PRR), and designing a tool for generation of dynamic graph datasets.}}




\subsection{Influence to Design, Performance, or Use of future GPUs}

\begin{itemize}[noitemsep, leftmargin=*]
  \item Dynamic Graph algorithms perform a significant amount of indirect memory access \cite{memory-yu15}. This can be optimized through the design of additional PTX instructions that optimize such memory accesses.
  \item Our algorithms pre-allocate a significant amount of memory beforehand to avoid performance bottlenecks due to CUDA's inbuilt memory allocator. Optimizing and parallelizing the memory allocator would allow the same GPU to run on larger problems.
\end{itemize}
