\begin{itemize}[noitemsep, leftmargin=*]
  \item \textbf{Programming Languages}:
    \href{https://github.com/puzzlef}{C/C++},
    \href{https://github.com/javascriptf}{JavaScript/TypeScript} (\href{https://github.com/nodef}{Node.js}/\href{https://github.com/htmlf}{Web}),
    \href{https://github.com/elmw}{Elm},
    \href{https://github.com/racketf}{Racket},
    \href{https://github.com/interpreterz}{Haskell},
    \href{https://github.com/matlabf}{MATLAB},
    \href{https://github.com/javaf}{Java},
    \href{https://github.com/processingf}{Processing},
    \href{https://github.com/python3f}{Python},
    \href{https://github.com/winp}{C\#},
    \href{https://github.com/qb40}{QuickBASIC},
    \href{https://github.com/bashf}{Bash},
    \href{https://github.com/vhdlf}{VHDL},
    \href{https://github.com/htmlf}{HTML},
    CSS, PostgreSQL, and SQLite.
  \item \textbf{High Performance Computing}:
    Platforms: OpenMP, Pthreads, CUDA, MPI;
    Systems: Intel Xeon, AMD EPYC, NVIDIA V100/A100;
    Environments: CentOS, Ubuntu;
    Job scheduling: SLURM;
    Data visualization: Google Sheets, Gnuplot.
  \item \textbf{Embedded Systems}:
    Microcontrollers: ESP32, Raspberry Pi, Arduino, AVR, 8086, 8051;
    Protocols: ZigBee, SPI, I2C, UART/RS232;
    Circuit Design: \href{https://github.com/electronicsf}{MultiSim}, LabVIEW, EAGLE;
    Test equipments: Multimeter, Oscilloscope, Function generator.
  \item \textbf{Web Technologies}:
    Client side: WebSocket, Web Storage, Angular, OAuth, REST, CORS, SPA, MVC, AJAX, JSON, XML;
    Server Side: Socket.IO, Express.js, Puppeteer, Lunr, Node.js.
  \item \textbf{Other Tools and Technologies}:
    Automation tools: GitHub Actions, Travis CI, Coveralls, Code Climate, Heroku, Docker, Git;
    Networking: TCP/UDP, gRPC, ZeroMQ;
    Image processing: MATLAB, OpenCV, FFMPEG;
    Signal processing: MATLAB, Simulink, MultiSim;
    Language understanding: WordNet;
    Machine learning: Tensorflow.
  \item \textbf{Personal Qualities}:
    Enjoy problem-solving and planning.
    Continuous improvement and positive attitude.
    Can work collaboratively and independently.
\end{itemize}
