\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}

\title{Curriculum Vitae}
\author{Subhajit Sahu}
\date{}
\maketitle

\section*{Summary}
Motivated and accomplished Ph.D. candidate in Computer Science and Engineering with a focus on designing efficient dynamic graph algorithms for social networks. Currently pursuing research under the guidance of \href{https://faculty.iiit.ac.in/~kkishore/}{Prof. Kishore Kothapalli} at the \href{https://cstar.iiit.ac.in}{Center for Security, Theory, and Algorithmic Research (CSTAR)}, IIIT Hyderabad, India. Proven track record in academia, industry, and open-source contributions. Demonstrated expertise in parallel algorithm design, dynamic graph analysis, and GPU-based graph analytics.

\section*{Education}
\textbf{Doctorate in Computer Science and Engineering} \\
\emph{Spring 2019 - Ongoing} \\
\href{https://cstar.iiit.ac.in}{Center for Security, Theory, and Algorithmic Research (CSTAR)}, IIIT Hyderabad, India - 500 032 \\
\emph{Thesis Advisor: \href{https://faculty.iiit.ac.in/~kkishore/}{Prof. Kishore Kothapalli}} \\
- Research Focus: Efficient Dynamic Graph Algorithms for Social Networks \\
- CGPA: 8.4 out of 10 [\href{https://drive.google.com/file/d/1c9goUgwXkyhsWIOc873RDhTk7nEs-hJ5/view?usp=sharing}{View CGPA}]

\section*{Professional Experience}
\textbf{Qualcomm, Hyderabad, India} \\
\emph{Role: Debugging Engineer - Android Graphics Driver} \\
\emph{Duration: 2016 - 2017}

\textbf{Verizon, Hyderabad, India} \\
\emph{Role: Portal Upgrade and RFID-based Snacks Automation System Design} \\
\emph{Duration: 2014 - 2015}

\section*{Research Results to Date}
\begin{itemize}[noitemsep, leftmargin=*]
  \item \textbf{Dynamic PageRank Algorithms:}
    \begin{itemize}[noitemsep, leftmargin=*]
      \item Designed two new parallel algorithms for updating PageRank in dynamic graphs.
      \item Achieved significant performance improvements over existing static and dynamic update algorithms on both CPU and GPU architectures.
    \end{itemize}
  \item \textbf{Dynamic Frontier Approach:}
    \begin{itemize}[noitemsep, leftmargin=*]
      \item Developed a low-overhead generalized parallel algorithm for incrementally identifying affected vertices in batch dynamic settings.
      \item Applied the approach to high-quality Louvain and high-speed LPA community detection algorithms, achieving notable speedups.
    \end{itemize}
  \item \textbf{Barrier-free PageRank:}
    \begin{itemize}[noitemsep, leftmargin=*]
      \item Applied Dynamic Frontier approach to improve Barrier-free PageRank implementation, achieving fault-tolerance and high performance.
      \item Demonstrated superiority over existing dynamic approaches in terms of speed and fault tolerance.
    \end{itemize}
\end{itemize}

\section*{Publication Track Record}
\begin{itemize}[noitemsep, leftmargin=*]
  \item Subhajit Sahu, Kishore Kothapalli, and Dip Sankar Banerjee. ``Dynamic Batch Parallel Algorithms for Updating PageRank." 2022 IEEE International Parallel and Distributed Processing Symposium Workshops (IPDPSW). IEEE, 2022.
  \item Subhajit Sahu, Kishore Kothapalli, Hemalatha Eedi, and Sathya Peri. ``Lock-Free Computation of PageRank in Dynamic Graphs." [Submitted].
  \item Subhajit Sahu, Kishore Kothapalli, and Dip Sankar Banerjee. ``Shared-Memory Parallel Algorithms for Community Detection in Dynamic Graphs." [Submitted].
\end{itemize}

\section*{Independent Projects}
\subsection*{Research Tools and Scripts}
\begin{itemize}[noitemsep, leftmargin=*]
  \item \href{https://github.com/nodef/nvgraph.sh}{CLI for nvGraph}: GPU-based graph analytics library by NVIDIA, using CUDA.
  \item \href{https://github.com/nodef/snap-data.sh}{CLI for SNAP dataset}: Collection of more than 50 large networks.
\end{itemize}

\subsection*{Open Source Contributions}
\begin{itemize}[noitemsep, leftmargin=*]
  \item \href{https://ifct2017.github.io}{Natural Language Query System for Indian Food Composition Tables 2017}.
  \item \href{https://github.com/nodef/extra-fyers}{Facade API for FYERS Securities}.
  \item \href{https://github.com/nodef/extra-array}{Array} and \href{https://github.com/nodef/extra-string}{String} Manipulation Utilities.
  \item \href{https://github.com/nodef/nvgraph.sh}{CLI for nvGraph}.
\end{itemize}

\section*{Skills}
\begin{itemize}[noitemsep, leftmargin=*]
  \item \textbf{Programming Languages:} Proficient in C++, JavaScript (Node.js/Web), Racket, Haskell, Java, MATLAB, MultiSim, Processing, Python. Experience in gRPC, ZeroMQ, Tensorflow.
  \item \textbf{Tools and Technologies:} HPC Job Scheduling: SLURM. Networking: Cisco/Dell, DNS, DHCP, Authentication. Cloud Environments: GCP, AWS, Azure. Deployment and Automation Tools: xCAT, Ansible.
  \item \textbf{Personal Qualities:} Analytical and Problem-Solving Skills. Continuous Improvement and Positive Attitude. Effective Communication at All Levels. Ability to Build Relationships. Team Collaboration and Independence.
\end{itemize}

\section*{Why Subhajit?}
\begin{itemize}[noitemsep, leftmargin=*]
  \item Proven researcher with impactful contributions to dynamic graph algorithms.
  \item Diverse experience in industry, academia, and open-source projects.
  \item Skillful in a range of programming languages and tools.
  \item Effective communicator and collaborator with a positive attitude.
\end{itemize}

\section*{What Subhajit Seeks}
Opportunity to contribute expertise in dynamic graph algorithms, parallel computing, and GPU-based analytics. Keen to engage in challenging research, collaborative projects, and innovation in a dynamic work environment.

\section*{What Subhajit Offers}
\begin{itemize}[noitemsep, leftmargin=*]
  \item Expertise in designing and implementing efficient parallel algorithms for dynamic graph analysis.
  \item Strong programming skills across various languages and platforms.
  \item Proven ability to lead and contribute to research projects.
  \item Open-source contributor with a passion for continuous learning and improvement.
\end{itemize}

\section*{Contact Information}
\begin{itemize}[noitemsep, leftmargin=*]
  \item \textbf{Email:} \href{mailto:subhajit.sahu@email.com}{subhajit.sahu@email.com}
  \item \textbf{LinkedIn:} \href{https://www.linkedin.com/in/subhajitsahu}{linkedin.com/in/subhajitsahu}
  \item \textbf{GitHub:} \href{https://github.com/nodef}{github.com/nodef}
\end{itemize}

\end{document}
